---
title: "Map generator"
---
This file generates the png's used in the weather map.

There are some big outliers that reduce the precision of the colors. Floor/ceiling points that are outside [.025, .975].




## Plot generator fn
```{r, message=F}
library(maptools); library(sp); library(gstat); library(ggplot2); library(png); library(readr); library(tidyverse)

MYC_original <- read_csv("data/MYC.csv")

choices_yearmon <- unique(MYC_original$date)#[1:3] 

states <- readShapePoly("data/statesp020.shp")

MYC <- MYC_original # MYC will be altered, floor and ceiling pts
```

Add or remove this line to generate names, and then change write name:
```{r}
  geom_text(data = MYC, aes(label=city, x = long, y = lat), 
            size=1.6, nudge_x = 2, nudge_y = .1) +

```

```{r}
# Temperature, original dataset it altered!

summary(MYC_original$Temp_mae)
quantile(MYC_original$Temp_mae, .975) #returns 6.5
MYC$Temp_mae[MYC$Temp_mae > 6.5] <- 6.5


generateMaps <- function(){

  # min/max coords of the interpolation area
  x.range <- as.numeric(c(-127, -65))
  y.range <- as.numeric(c(23, 51))
  
  grd <- expand.grid(x = seq(from = x.range[1], to = x.range[2], by = 0.1), y = seq(from = y.range[1], 
      to = y.range[2], by = 0.1))  # creates grid of points, according to grid extent
  coordinates(grd) <- ~x + y
  gridded(grd) <- TRUE #promotes non-gridded structure to gridded
  
  for (yearmon in choices_yearmon){
    writeLines(yearmon)
    ds <- filter(MYC, date == yearmon)
    ds_coords <- ds
    coordinates(ds_coords) <- ~long + lat
    
    # Calculate interpolation
    idw <- idw(formula = Temp_mae ~ 1, locations = ds_coords, 
      newdata = grd)
  
    idw.output <- as.data.frame(idw)
    names(idw.output)[1:3] <- c("long", "lat", "var1.pred")
    
    idw.output <- idw.output[ , -4]
    
    m <- ggplot() + 
    geom_tile(data = idw.output, alpha = 0.8, aes(x = long, y = lat, 
      fill = round(var1.pred, 0))) + 
    coord_cartesian(xlim = c(-127, -65), ylim = c(23, 51)) +
    scale_fill_gradientn(colors = c("#FFFFFF", "#ffffb2", "#9e9ac8"), limits = c(0,6.5)) + 
    geom_path(data = states, aes(long, lat, group = group), colour = "grey") +
    geom_point(data = ds, aes(x = long, y = lat), shape = 21, 
          colour = "red") + 

    labs(fill = "MAE") +
    theme(legend.position = c(.5, .02), #(x,y)
          legend.direction = "horizontal",
          plot.margin=grid::unit(c(-3,-8.5, 6,-8.8), "mm"),
          axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.background=element_blank(),
          panel.border=element_blank(),
          panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          plot.background=element_blank())
    
    writeLines("Saving...")
    ggsave(filename = paste(yearmon, ".png", sep = ""), plot = m,
      width = 18, height = 12, 
       units = "cm", 
       dpi = 300,
      path = "www")
  }
  writeLines("End")
}

generateMaps()
```













# For rain maps

Exploratory
```{r}
MYC_original <- MYC # backup

ggplot(MYC) + geom_density(aes(x=RainError))

quantile(MYC$RainError, c(.025, .975)) #returns (-13.36706,  13.58171)
MYC$RainError[MYC$RainError > 15] <- 15
MYC$RainError[MYC$RainError < -15] <- -15

ggplot(MYC) + geom_density(aes(x=RainError))
```

```{r}
# Rain, make sure to reload data set after
summary(MYC_original$RainError)
quantile(MYC_original$RainError, c(.025, .975)) # returns (-18.63563,  17.90400)
MYC$RainError[MYC$RainError > 20] <- 20
MYC$RainError[MYC$RainError < -20] <- -20

generateMaps <- function(){

  # min/max coords of the interpolation area
  x.range <- as.numeric(c(-127, -65))
  y.range <- as.numeric(c(23, 51))
  
  grd <- expand.grid(x = seq(from = x.range[1], to = x.range[2], by = 0.1), y = seq(from = y.range[1], 
      to = y.range[2], by = 0.1))  # creates grid of points, according to grid extent
  coordinates(grd) <- ~x + y
  gridded(grd) <- TRUE #promotes non-gridded structure to gridded
  
  for (yearmon in choices_yearmon){
    writeLines(yearmon)
    ds <- filter(MYC, date == yearmon)
    ds_coords <- ds
    coordinates(ds_coords) <- ~long + lat
    
    # Calculate interpolation
    idw <- idw(formula = RainError ~ 1, locations = ds_coords, 
      newdata = grd)
  
    idw.output <- as.data.frame(idw)
    names(idw.output)[1:3] <- c("long", "lat", "var1.pred")
    
    idw.output <- idw.output[ , -4]
    
    m <- ggplot() + 
    geom_tile(data = idw.output, alpha = 0.8, aes(x = long, y = lat, 
      fill = round(var1.pred, 0))) + 
    coord_cartesian(xlim = c(-127, -65), ylim = c(23, 51)) +
    scale_fill_gradientn(colors = c("#fc8d59", "#fdcc8a", "white", "#92c5de", "#0571b0"), limits = c(-20,20)) + 
    geom_path(data = states, aes(long, lat, group = group), colour = "grey") +
    geom_point(data = ds, aes(x = long, y = lat), shape = 21, 
          colour = "red") + 
    geom_text(data = MYC, aes(label=city, x = long, y = lat), 
              size=1.6, nudge_x = 2, nudge_y = .1) +
    labs(fill = "Rain Error") +
    theme(legend.position = c(.5, .02), #(x,y)
          legend.direction = "horizontal",
          plot.margin=grid::unit(c(-3,-8.5, 6,-8.8), "mm"),
          axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.background=element_blank(),
          panel.border=element_blank(),
          panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          plot.background=element_blank())
    
    writeLines("Saving...")
    ggsave(filename = paste(yearmon, "_rain_names.png", sep = ""), plot = m,
      width = 18, height = 12, 
       units = "cm", 
       dpi = 300,
      path = "www")
  }
  writeLines("End")
}

generateMaps()
```


























Testers

## Import data
```{r}
# setwd("C:/Google Drive/CSUEB/data_expo/4")
library(readr); library(tidyverse)
MYC <- read_csv("data/MYC.csv")
MYC_nov <- MYC %>% filter(date == "Nov 2014")
MYC_test <- MYC_nov
```


## Base script for generating a map
### Import
```{r}
library(maptools); library(sp); library(gstat); library(ggplot2)
states <- readShapePoly("data/statesp020.shp")

coordinates(MYC_test) <- ~long + lat
```

### Interpolation
```{r}
# min/max coords of the interpolation area
x.range <- as.numeric(c(-127, -65))   # c(-125, -65.5)
y.range <- as.numeric(c(23, 51))      # c(24.2, 50)

grd <- expand.grid(x = seq(from = x.range[1], to = x.range[2], by = 0.1), y = seq(from = y.range[1], 
    to = y.range[2], by = 0.1))  # creates grid of points, according to grid extent
coordinates(grd) <- ~x + y
gridded(grd) <- TRUE #promotes non-gridded structure to gridded


idw <- idw(formula = MaxTemp_mae ~ 1, locations = MYC_test, 
    newdata = grd)  # apply idw model for the data

idw.output = as.data.frame(idw)  # output is defined as a data table
names(idw.output)[1:3] <- c("long", "lat", "var1.pred")

# Dropped a column that had all null values.
idw.output <- idw.output[ , -4]
```
```{r}
ggplot(data = MYC_nov) +
  geom_point(aes(x = long, y = lat), shape = 21, 
    colour = "red") +
  geom_text(aes(label=city, x = long, y = lat), 
            size=1.6, nudge_x = 2.3, nudge_y = .1)
```

### Make ggplot map
```{r}
m <- ggplot() + 
  geom_tile(data = idw.output, alpha = 0.8, aes(x = long, y = lat, 
    fill = round(var1.pred, 0))) + 
  coord_cartesian(xlim = c(-127, -65), ylim = c(23, 51)) +
  scale_fill_gradientn(colors = c("cyan", "orange"), limits = c(1,11)) +
  theme() + #(top, right, bottom, left)
  geom_path(data = states, aes(long, lat, group = group), colour = "grey") +
  geom_point(data = MYC_nov, aes(x = long, y = lat), shape = 21, 
        colour = "red") +
  #geom_text(data = MYC_nov, aes(label=city, x = long, y = lat), 
  #          size=1.7, nudge_x = 2, nudge_y = .1) +
  labs(fill = "MAE") +
  theme(legend.position = c(.5, .02), #(x,y)
        legend.direction = "horizontal",
        plot.margin=grid::unit(c(-3,-9, 6,-9), "mm"),
        axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        plot.background=element_blank())

m
```

testing ggsave()
```{r}
ggsave(filename = "nov 14.png", plot = m,
      width = 22, height = 12, 
       units = "cm", 
       dpi = 300,
      path = "pics")

ggsave(filename="myPlot.jpg", plot=lastplot(),
       width = 10, height = 5, 
       units = "cm", # other options are "in", "cm", "mm" 
       dpi = 200
       )
```
